\documentclass[11pt]{report}
\usepackage{graphicx}

\begin{document}

The Model:

We have two assets X and Y, which are tied are tied to the objective true value, (TV) but have a probability to  \textit{break-up} and thus no longer be tied to the true value. We conduct pairs-trading strategy on X and Y if difference in the prices of X and Y becomes greater than a given threshold, and we trade back when the prices converge back.

Input variables:

Convergence Rate (ConvRate)
Break Up Probability (BreakUpProb): Probability to break up on each individual turn.
Variance
Threshold: critical difference between X and Y after which is reached we enter trade.

In our study Variance and Threshold are direcly tied to Break Up Probability.

\begin{equation}
Variance = BreakUpProb * 100
\end{equation}

\begin{equation}
Threshold = BreakUpProb
\end{equation}

(It is probably more accurate to express BreakUpProb as a function of variance, but mathematically it is the same thing, and has no effect on the result of the simulation)

Definitions of X and Y:

Both X and Y start at 100, as well as the TV. 

X and Y operate exactly the same, also when X or Y are greater than the true value they receive an negative bump, and if they are less then the true value they get a positive bump. The above for cases can be illustrated with an example of just one:

For example if $x_i$ is less then $tv_i$:

\begin{equation}
detlaX_i = Uniform(-variance, variance)
\end{equation}

$deltaX_i$ is chosen from an uniform distributes that ranges between specifed values of variance.

\begin{equation}
detlaTV_i = Uniform(-variance, variance)
\end{equation}

$deltaTV_i$ is chosen from an uniform distributes that ranges between specifed values of variance.

\begin{equation}
tv_{i+i} = tv_i + deltaTV
\end{equation}


\begin{equation}
x_{i+i} = x_i + deltaX_{i} + (tv_i - x_i) * ConvRate
\end{equation}

Therefore, for non-zero value of \textit{ConvRate} X and expected 0 value of \textit{deltaX}, X is getting a bump and is tending towards convergence. 

Simulation:

Since Variance and Threshold are directly tied to Break Up Probability, we only have to independed variables. 




\end{document}
